Everest Bio

### 2021-10-26 00-ES/xar-EB-ES/xar-EB-ES.Rmd
reorganizando las vainas de los folderes

---
title: "Everest Bio"
subtitle: "Ecosystem services for Distributed recycling via Additive Manufacturing"  
author:
- "Fabio CRUZ"
date: '`r Sys.Date()`'
output:
  xaringan::moon_reader:
    css: xaringan-themer.css
    nature:
#      slideNumberFormat: "%current%"
      highlightStyle: github
      highlightLines: true
      ratio: 16:9
      countIncrementalSlides: true
      navigation:
        scroll: false # disable slide transitions by scrolling      
---

```{r packages, echo = FALSE, message=FALSE, warning=FALSE}
library(tidyverse)
library(xaringanExtra)
library(xaringanthemer)

@@

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
knitr::opts_chunk$set(
  fig.width=9, fig.height=3.5, fig.retina=3,
  out.width = "100%",
  cache = FALSE,
  echo = FALSE,
  message = FALSE, 
  warning = FALSE,
  fig.show = TRUE,
  hiline = TRUE,
  include = TRUE
)

#library(xaringanBuilder)
#build_pdf("ES-presentation.Rmd")

# xaringanExtra
xaringanExtra::use_panelset()
```

```{r xaringan-themer, include=FALSE, warning=FALSE}

style_duo_accent(
  primary_color = "#1381B0",
  secondary_color = "#FF961C",
  inverse_header_color = "#FFFFFF", 
  base_font_size = "24px",
  colors = c(
    red = "#f34213",
    purple = "#3e2f5b",
    orange = "#ff8811",
    green = "#d9edc2",
    white = "#FFFFFF",
    grey = "#F5F5F5"
  ),
   extra_css = list(
    ".remark-slide-content h1" = list(
      "margin-bottom" = 0, 
      "margin-top" = 0),
     ".remark-slide-content > h1:first-of-type" = list(
       "margin-top" = "5px",
       "margin-bottom" = "10px"
     ),
    ".remark-slide-content > h2:first-of-type" = list(
       "margin-top" = "5px",
       "margin-bottom" = "10px"
     ),
    ".remark-slide-content > h3:first-of-type" = list(
       "margin-top" = "5px",
       "margin-bottom" = "10px"
     ),
    ".remark-slide-content" = list (
        "padding-top" =  "25px",
        "padding-left" =  "50px",
        "padding-right" =  "50px",
        "padding-bottom" =  "25px"
    ),

    ".small" = list("font-size" = "90%"),

    ".Large , .Large .remark-code, .Large .remark-inline-code" = list("font-size"= "144%"), 
    ".large , .large .remark-code, .large .remark-inline-code" = list("font-size"= "120%"), 
    ".small , .small .remark-code, .small .remark-inline-code" = list("font-size"= "90%"), 
    ".footnotesize, 
    .footnotesize .remark-code, .footnotesize .remark-inline-code" = list( "font-size"= "80%"),

    ".scriptsize , .scriptsize .remark-code, .scriptsize .remark-inline-code" = list("font-size"= "70%"),
    ".tiny , .tiny .remark-code, .tiny .remark-inline-code" = list("font-size"= "60%"),

    ".footnote" = list (
        "position" =  "absolute",
        "bottom" =  "0",
        "padding-right" = "8em", # to avoid the page numbering 
        "font-size" =  "60%"
    ),
    ".fn" = list(
      "vertical-align" = "super",
      "font-size" = "60%",
      "color" = "purple"
    )

  )
)

@@

# Valorization of SE

@@

>>>>

---
title: "Everest Bio"
subtitle: "Ecosystem services for Distributed recycling via Additive Manufacturing"  
author:
- "Fabio CRUZ"
date: '`r Sys.Date()`'
output:
  xaringan::moon_reader:
    css: xaringan-themer.css
    seal: false
    nature:
#      slideNumberFormat: "%current%"
      highlightStyle: github
      highlightLines: true
      ratio: 16:9
      countIncrementalSlides: true
      navigation:
        scroll: false # disable slide transitions by scrolling
always_allow_html: true
---

```{r setup, echo = FALSE, message=FALSE, warning=FALSE}
library(tidyverse)
library(xaringanExtra)
library(xaringanthemer)
library(fontawesome)
library(readxl)
library(here)

source("xaringan-themer.R")

options(htmltools.dir.version = FALSE)
knitr::opts_chunk$set(
  fig.width=9, fig.height=3.5, fig.retina=3,
  out.width = "100%",
  cache = FALSE,
  echo = FALSE,
  message = FALSE, 
  warning = FALSE,
  fig.show = TRUE,
  hiline = TRUE,
  include = TRUE
)

#library(xaringanBuilder)
#build_pdf("index.Rmd")

# xaringanExtra
xaringanExtra::use_panelset()

#xaringanExtra::use_share_again()

## Loading data
CICES <- read_excel(here("../../data/CICES/Finalised-V5.1_18032018.xlsx"), sheet = "CICES V5.1",  skip = 4 )

@@

class: title-slide, left, bottom

```{r, out.width = '250px', fig.align='right'}
knitr::include_graphics(paste0(URL, 'Logos/ERPI/UL-ERPI.png'))
```

`r fa("map-marker-alt", fill = "steelblue")` `r rmarkdown::metadata$date`

# `r fa("comment", fill = "steelblue")` `r rmarkdown::metadata$title`

`r fa("user-friends", fill = "steelblue")` `r rmarkdown::metadata$subtitle`

@@

@@

---
# Tool for Everest Bio

.pull-left[
## Goal:
The main foal of the tool will be the identification of ES that are priorities for an industrial system inside a Territory.
]

---
## Structure of the tool

1. Identification of the Territory
1. Two types of actors:
   1. Industrial Agent: **Identification of LCI of the Process**
   1. Territorial Agent: **Identification of the Urban ES priorities**

class: middle

# CICES

1. .large.bg-yellow[Provisioning Services (biotic & Abiotic)]
1. .large.bg-yellow[Regulation & Maintenance (biotic & Abiotic)]
1. .large.bg-yellow[Cultural]

# Provisioning Services (biotic & Abiotic)
## Plants

.pull-left[
**Territorial Question**

*Are cultivated plants (Terrestrial or Aquatic) strategic for the territory for nutrition, materials or energy ?*	
]

.pull-right[
**Industrial Question**

*Are cultivated plants (Terrestrial or Aquatic) impacted in certain level by the use of your technology or proposition ?*

```{r}

library(kableExtra)
# Version Flextable
# CICES_filter <- function(ID, size = 15, ...)
# {
#   Table <- CICES %>% select(Group, Class, Code) %>% 
#   filter(Code %in% ID) %>% 
#   flextable() %>% 
#   merge_v( j = "Group") %>% 
#   fontsize(size = size,  part = "all") %>% 
#   width(width = c(2,8,1))
#   return(Table)
# }

# Version Kableextrs
CICES_filter <- function(ID, size = 15, ...)
{
  Table <- 
    CICES %>% select(Group, Class, Code, 'Example Service') %>% 
    filter(Code %in% ID) %>% 
    kbl() %>%
    #kable_paper("striped", full_width = TRUE) %>% 
    kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), font_size = size)  %>% 
  collapse_rows(columns = 1:1)

  return(Table)
}

CICES_filter(ID=c("1.1.1.1", "1.1.1.2", "1.1.1.3", 
                     "1.1.2.1", "1.1.2.2", "1.1.2.3"), size = 15)

---
# Provisioning Services (biotic & Abiotic)
## Animals

.pull-left[
**Territorial Question**

*Are Reared animals (Terrestrial or Aquatic) strategic for the territory for nutrition, materials or energy ?*	
]

.pull-right[
**Industrial Question**

*Are Reared animals (Terrestrial or Aquatic) strategic for the territory for nutrition, materials or energy ?*
]

```{r}
CICES_filter(ID=c("1.1.3.1", "1.1.3.2", "1.1.3.3", "1.1.4.1", "1.1.4.2", "1.1.4.3"), size = 15)
```

# Provisioning Services (biotic & Abiotic)
## Wild Animals & Plants

.pull-left[
**Territorial Question**

*Are Reared animals (Terrestrial or Aquatic) strategic for the territory for nutrition, materials or energy ?*	
]

.pull-right[
**Industrial Question**

*Are Reared animals (Terrestrial or Aquatic) strategic for the territory for nutrition, materials or energy ?*
]

```{r}
CICES_filter(ID=c("1.1.5.1","1.1.5.2","1.1.5.3","1.1.6.1","1.1.6.2","1.1.6.3"), size = 13)
```

---
# Provisioning Services (biotic & Abiotic)
## Genetic Material

.pull-left[
**Territorial Question**

*Is the Genetic material from plants, algae or fungi (including seed, spore or gamete production) an important element for the territory ?*	]

.pull-right[
**Industrial Question**

*Is the Genetic material from plants, algae or fungi (including seed, spore or gamete production) affected by the use of your technology int the territory ?*
]

```{r}
CICES_filter(ID=c("1.2.1.1","1.2.1.2","1.2.1.3","1.2.2.1","1.2.2.2","1.2.2.3"), size = 15)
```

# Provisioning Services (biotic & Abiotic)
## Water

.pull-left[
**Territorial Question**

*Is Water (for nutrition, materials or energy) an issue for the territory?*	]

.pull-right[
**Industrial Question**

*The is the impact of LCI?*
]

```{r ES_Provision_water}
CICES_filter(ID=c("4.2.1.1", "4.2.1.2", "4.2.1.3", "4.2.1.4", "4.2.2.1", "4.2.2.2", "4.2.2.3"
), size = 15)
```

# Provisioning Services (biotic & Abiotic)
## Others Abiotic

```{r ES_Provision_Abiotic}
#CICES_filter(ID=c("4.3.1.1","4.3.1.2","4.3.1.3","4.3.2.1","4.3.2.2","4.3.2.3","4.3.2.4","4.3.2.5","4.3.2.6"), size = 12)

CICES_filter(ID=c("4.3.1.1","4.3.1.2","4.3.1.3","4.3.2.1","4.3.2.2","4.3.2.3","4.3.2.4","4.3.2.5","4.3.2.6"), size = 15)

class: middle

# CICES

1. .large.bg-yellow[Provisioning Services (biotic & Abiotic)]
1. .large.bg-yellow[Regulation & Maintenance (biotic & Abiotic)]
1. .large.bg-yellow[Cultural]

# Regulation & Maintenance (biotic & Abiotic)

## Biochemical or physical inputs to ecosystems

.pull-left[
**Territorial Question**

*Is*	]

.pull-right[
**Industrial Question**

*The *
]

```{r}
#CICES_filter(ID=c("4.3.1.1","4.3.1.2","4.3.1.3","4.3.2.1","4.3.2.2","4.3.2.3","4.3.2.4","4.3.2.5","4.3.2.6"), size = 12)

CICES_filter(ID=c("2.1.1.1", "2.1.1.2", "2.1.2.1", "2.1.2.2", "2.1.2.3"), size = 15)

# Regulation & Maintenance (biotic & Abiotic)
## Regulation of physical, chemical, biological conditions

.pull-left[
**Territorial Question**

*Is*	]

.pull-right[
**Industrial Question**

*The *
]

```{r}
#CICES_filter(ID=c("4.3.1.1","4.3.1.2","4.3.1.3","4.3.2.1","4.3.2.2","4.3.2.3","4.3.2.4","4.3.2.5","4.3.2.6"), size = 12)

CICES_filter(ID=c("2.2.1.1", "2.2.1.2", "2.2.1.3", "2.2.1.4", "2.2.1.5" ), size = 15)

# Regulation & Maintenance (biotic & Abiotic)
## Regulation of physical, chemical, biological conditions

.pull-left[
**Territorial Question**

*Is*	]

.pull-right[
**Industrial Question**

*The *
]

```{r}
#CICES_filter(ID=c("4.3.1.1","4.3.1.2","4.3.1.3","4.3.2.1","4.3.2.2","4.3.2.3","4.3.2.4","4.3.2.5","4.3.2.6"), size = 12)

CICES_filter(ID=c("2.2.2.1", "2.2.2.2", "2.2.2.3", "2.2.3.1", "2.2.3.2", "2.2.4.1", "2.2.4.2", "2.2.5.1", "2.2.5.2", "2.2.6.1", "2.2.6.2" ), size = 15)

# Regulation & Maintenance (biotic & Abiotic)
## Regulation of physical, chemical, biological conditions

.pull-left[
**Territorial Question**

*Is*	]

.pull-right[
**Industrial Question**

*The *
]

```{r}
#CICES_filter(ID=c("4.3.1.1","4.3.1.2","4.3.1.3","4.3.2.1","4.3.2.2","4.3.2.3","4.3.2.4","4.3.2.5","4.3.2.6"), size = 12)

CICES_filter(ID=c("2.2.4.1", "2.2.4.2", "2.2.5.1", "2.2.5.2", "2.2.6.1", "2.2.6.2" ), size = 15)
```

# CICES

1. .large.bg-yellow[Provisioning Services (biotic & Abiotic)]
1. .large.bg-yellow[Regulation & Maintenance (biotic & Abiotic)]
1. .large.blue[Cultural]

# Cultural (Biotic) 
## Direct contact with Nature

.pull-left[
**Territorial Question**

*Is*	]

.pull-right[
**Industrial Question**

*The *
]

```{r}
CICES_filter(ID=c("3.1.1.1", "3.1.1.2", "3.1.2.1", "3.1.2.2", "3.1.2.3", "3.1.2.4"), size = 15)
```

# Cultural (Biotic) 
## Indirect contact with Nature

.pull-left[
**Territorial Question**

*Is*	]

.pull-right[
**Industrial Question**

*The *
]

```{r}
CICES_filter(ID=c("3.2.1.1","3.2.1.2","3.2.1.3","3.2.2.1","3.2.2.2"), size = 15)

# Cultural (Abiotic) 
## Direct and Indirect link with Nature

.pull-left[
**Territorial Question**

*Is*	]

.pull-right[
**Industrial Question**

*The *
]

```{r}
CICES_filter(ID=c("6.1.1.1","6.1.2.1","6.2.1.1","6.2.2.1"), size = 15)
```

Thanks
